### 2020-10-18 Analysis/Code/Sorokin_JMP_2020.Rmd
Misc

star.out<-stargazer(reg1, reg3,
                    label = "scoreDifTransDiscReg",
                    header = FALSE,
                    title = "Discounts Before Potential Transitions And Firm Heterogeneity",
                    se=list(se1, se3),
                    dep.var.labels = c("$\\mathbb{P}(Discount)$"),
                    column.labels=c("OLS", "FE"),
                    model.numbers = F,
                    omit = c("tWODisc", "reviews", "noScore", "realPositive",
                             "mPositive", "vPositive", "age", "young", "Constant",
                             "score", "day", "week", "needPosDays", "needNegDays"),
                    covariate.labels = c("Pos. Transition", "Neg. Transition",
                                         "Score Difference",
                                         "S. Diff $\\times$ Pos. Tr.",
                                         "S. Diff $\\times$ Neg. Tr."),
                    order = c("treatment","sdif"),
                    omit.stat=c("f","adj.rsq","ser"),
                    no.space=T)
```

@@

```{r results = 'asis'}
cat(star_insert_row(star.out, c("Weekdays + Week Effects & $\\checkmark$  & $\\checkmark$  \\\\",
                                "Game Effects & $\\checkmark$  & $\\checkmark$ \\\\"), 
                    insert.after = c(28,28)))
```
\newpage

>>>>

star.out<-stargazer(reg1, reg3,
                    label = "scoreDifTransDiscReg",
                    header = FALSE,
                    title = "Discounts Before Potential Transitions And Firm Heterogeneity",
                    se=list(se1, se3),
                    dep.var.labels = c("$\\mathbb{P}(Discount)$"),
                    column.labels=c("OLS", "FE"),
                    model.numbers = F,
                    omit = c("tWODisc", "reviews", "noScore", "realPositive",
                             "mPositive", "vPositive", "age", "young", "Constant",
                             "score", "day", "week", "needPosDays", "needNegDays"),
                    covariate.labels = c("Pos. Transition", "Neg. Transition",
                                         "S. Diff $\\times$ Pos. Tr.",
                                         "S. Diff $\\times$ Neg. Tr.",
                                         "Score Difference"),
                    order = c("treatment","sdif"),
                    omit.stat=c("f","adj.rsq","ser"),
                    no.space=T)
```

@@

```{r results = 'asis'}
cat(star_insert_row(star.out, c("Weekdays + Week Effects & $\\checkmark$  & $\\checkmark$ & $\\checkmark$  \\\\",
                                "Game Effects & $\\checkmark$  & $\\checkmark$ & $\\checkmark$ \\\\"), 
                    insert.after = c(28,28)))
```
\newpage
